Real Estate

### 2022-10-31 src/real_estate.Rmd
normalized data

```{r}
```

```{r}
# calculate income to home price
```

```{r}
# normalize columns into new data table
n_MSA_realEstate_data <- MSA_realEstate_data %>% 
  # normalize population data
  mutate(n_pop_change = (pop_percent_change20_21 - min(pop_percent_change20_21))/(max(pop_percent_change20_21)-min(pop_percent_change20_21))) %>% 
  # normalize employment growth
  mutate(n_employ_change = (employment_yo_y21_22 - min(employment_yo_y21_22)) / (max(employment_yo_y21_22) - min(employment_yo_y21_22))) %>% 
  # normalize rent to income
  mutate(n_rent_to_income = (rent_to_income- min(rent_to_income)) / (max(rent_to_income) - min(rent_to_income))) %>% 
  # normalize income to home price
  mutate(n_income_to_homeprice = (income_to_homeprice - min(income_to_homeprice)) / (max(income_to_homeprice) - min(income_to_homeprice)))

@@

```{r}
# invert normalized rent to income ratio so lower values (more favorable) have higher scores

= 1- normalized score
```

```{r}
# weights from owen

# place holder column
MSA_real_estate_score <- 
  mutate

weights <- c()

@@

>>>>

```{r}
# normalize columns into new data table
MSA_realEstate_data <- MSA_realEstate_data %>% 
  # normalize population data
  mutate(n_pop_change = (pop_percent_change20_21 - min(pop_percent_change20_21))/(max(pop_percent_change20_21)-min(pop_percent_change20_21))) %>% 
  # normalize employment growth
  mutate(n_employ_change = (employment_yo_y21_22 - min(employment_yo_y21_22)) / (max(employment_yo_y21_22) - min(employment_yo_y21_22))) %>% 
  # normalize rent to income
  mutate(n_rent_to_income = (rent_to_income- min(rent_to_income)) / (max(rent_to_income) - min(rent_to_income))) %>% 
  # normalize income to home price
  mutate(n_income_to_homeprice = (income_to_homeprice - min(income_to_homeprice)) / (max(income_to_homeprice) - min(income_to_homeprice)))

@@

```{r}
# invert normalized rent to income ratio so lower values (more favorable) have higher scores
MSA_realEstate_data <- MSA_realEstate_data %>% 
  mutate(income_to_rent_inverted = 1 - n_income_to_rent)

@@

```{r}
# weights from owen
real_estate_weights <- c()

#make real_estate_score column
MSA_realEstate_data <- MSA_realEstate_data %>% 
  mutate(real_estate_score = MSA) #this is just a place holder
```

```{r}
size <- dim(MSA_realEstate_data)

for (i in 1:size[1]) {
  MSA_x_data <- c(MSA_realEstate_data$eviction_notice_days_normalized_inverted[i],
                  MSA_realEstate_data$security_depopsit_limit_num[i],
                  MSA_realEstate_data$notice_for_entry_days_num[i]
                  )
  MSA_realEstate_data$real_estate_score[i] = weighted.mean(MSA_x_data, real_estate_weights)
  }
```
